---
output: pdf_document
---

###Simulations
# The exponential distribution can be simulated in R with rexp(n, lambda) where lambda is the rate parameter. The mean of exponential distribution is 1/lambda and the standard deviation is also 1/lambda. For these simulations, we set lambda to 0.2. We investigate the distribution of averages of 40 exponentials. For this purpose, we perform a thousand or so simulated averages of 40 exponentials.
```{r}
setwd("D:/Programming/GitHub/coursera-statinference/assignment1")

n <- 40
lambda <- 0.2
reps <- 1000

Exp <- 0
for (i in 1:reps) 
{
  Exp <- Exp + rexp(n,lambda)
}
Exp <- Exp / reps

summary(Exp)

###Results
#1. Show where the distribution is centered at and compare it to the theoretical center of the distribution.
#theoretical mean = 1/lambda = 5
#simulated mean:
mean <- mean(Exp)
mean
```

#2. Show how variable it is and compare it to the theoretical variance of the distribution.
```{r}
#theoretical variance = lambda^-2 = 0.04
#simulated variance:
1/(mean(Exp))^2
```

#3. Show that the distribution is approximately normal.
```{r}
h <- hist(Exp,freq=FALSE)
xfit<-seq(min(Exp),max(Exp),length=40) 
yfit<-dnorm(xfit,mean=mean(Exp),sd=sd(Exp)) 
yfit <- yfit*diff(h$mids[1:2])*length(Exp) 
plot(h, main="Comparison to Normal Distribution")
lines(xfit, yfit, col="blue", lwd=2)
abline(v=1/lambda,col="blue")
abline(v=mean,col="green")

qqnorm(Exp)
qqline(Exp)
```

#4. Evaluate the coverage of the confidence interval for 1/lambda
```{r}
left <- mean - qt(.95,40)*sd(Exp)/sqrt(n)
right <- mean + qt(.95,40)*sd(Exp)/sqrt(n)
left
right

```
